Optimal (Multiway) Spatial Joins

### 2024-06-03 msj.tex
yufei

\extraspacing {\bf Terminology.} Each point $(x, y)$ is said to {\em define} a y-coordinate $y$, a horizontal segment $[x_1, x_2] \times y$ is said to {\em define} a y-coordinate $y$, and each rectangle $r = [x_1, x_2] \times [y_1, y_2]$ is said to {\em define} two y-coordinates $y_1$ and $y_2$. These definitions permit us to convenient specify a set of y-coordinates using expressions like ``the set of four y-coordinates defined by point $p$, horizontal segment $h$, and rectangle $r$''.

>>>>

\extraspacing {\bf Terminology.} Each point $(x, y)$ is said to {\em define} a y-coordinate $y$, a horizontal segment $[x_1, x_2] \times y$ is said to {\em define} a y-coordinate $y$, and each rectangle $r = [x_1, x_2] \times [y_1, y_2]$ is said to {\em define} two y-coordinates $y_1$ and $y_2$. These definitions permit us to conveniently specify a set of y-coordinates using expressions like ``the set of four y-coordinates defined by point $p$, horizontal segment $h$, and rectangle $r$''.
